Operational Performance Analyses at European Airports with Community-Collected Open Data

### 2020-03-05 paper01.Rmd
worked on exporting paper to ICNS template

---
title: "Operational Performance Analyses at European Airports with Community-Collected Open Data"
author: "RQ"
date: "02/02/2020"
output:
  bookdown::pdf_document2:
    toc: false
  html_document:
    df_print: paged
  word_document: default
abstract: My abstract
bibliography: paperxx.bib
---

@@

Within air transportation and air traffic management research the concept of reproducibility is still in its early infancy stage.
The topic was first articulated at the 2017 ATM Seminar.
Spinielli and Koelle published a paper demonstrating the replicability of the research pipeline in XXX. The paper and its underlying data is openly available via https://XXX.
During the SESAR Innovation Days, December 2019, a wider discussion took place about the availability of data for research.

@@

>>>>

---
title: "Operational Performance Analyses at European Airports with Community-Collected Open Data"
author: "Antonio Lazarovski, Enrico Spinielli, and Rainer Koelle, EUROCONTROL, Brussels, Belgium"
# date: "02/02/2020"
output:
  bookdown::word_document2:
    reference_docx: tmpl-ref.docx
  word_document: default
  html_document:
    df_print: paged
  bookdown::pdf_document2:
    toc: false
abstract: My abstract
bibliography: paperxx.bib
---

@@

Within air transportation and air traffic management research the concept of reproducibility is still in its early infancy stage.
The topic was first articulated at the 2017 ATM Seminar.
Spinielli and Koelle published a paper demonstrating the replicability of the research pipeline in XXX. The paper and its underlying data is openly available via https://github.com/rainer-rq-koelle/paper-2020-ICNS.
During the SESAR Innovation Days, December 2019, a wider discussion took place about the availability of data for research.

@@

## Trajectory Data Coverage

For this study data from Opensky Network was downloaded for Frankfurt Rhine/Main airport, EDDF.
The downloaded data covered a period of XX weeks, i.e. 22. April - XX May.

```{r}

```

The ADSB trajectory data is downloaded from Opensky Network in form of so-called *state vectors*.
A state vector comprises the information associated with the aircraft ICAO 24-bit address.
It represents a time-binned representation of the flight derived from ADSB and Mode-S messages.
The Opensky Network API is documented at https://opensky-network.org/apidoc/rest.html.

(ref:rolling-window) Determination of the Actual Take-Off Time

```{r rolling-window, fig.cap="(ref:rolling-window)", out.width="50%", fig.pos="h", echo=FALSE}
knitr::include_graphics("figures/rolling-window-mean.png")
```

Fig. \@ref:(fig:rolling-window) shows an example for the determination of the taxi-out time.
To counter the problem of noisy onground flags a sliding window technique has been used.
For the departure in question, DLH6RL, several extreme spikes have been observed.
